### 2016-09-28 architecture.tex
Fix line wrapping

Due to being written in pure Python without the use of extension modules,
SymPy's performance characteristics are generally poorer than
its commercial competitors. For many applications,
the performance of SymPy, as measured by clock cycles, memory usage, and memory
layout, is sufficient.
However, the boundaries for when SymPy's pure Python strategy becomes
insufficient are when the user requires handling of very long expressions or many
small expressions. Where this boundray lies depends on the system at hand, but tends
to be within the range of $O(10^4) - O(10^6)$ symbols for modern computers.

@@

SymPy has recently started to use SymEngine as an
optional backend, initially in \texttt{sympy.physics.mechanics} only.
Future work witll involve
allowing more algorithms in SymPy to use SymEngine as a backend.

>>>>

Due to being written in pure Python without the use of extension modules,
SymPy's performance characteristics are generally poorer than
its commercial competitors. For many applications,
the performance of SymPy, as measured by clock cycles, memory usage, and memory
layout, is sufficient.
However, the boundaries for when SymPy's pure Python strategy becomes
insufficient are when the user requires handling of very long expressions or many
small expressions. Where this boundray lies depends on the system at hand, but tends
to be within the range of $10^4$--$10^6$ symbols for modern computers.

@@

SymPy has recently started to use SymEngine as an
optional backend, initially in \texttt{sympy.\allowbreak{}physics.\allowbreak{}mechanics} only.
Future work witll involve
allowing more algorithms in SymPy to use SymEngine as a backend.
